### 2021-04-15 submission/manuscript.Rmd
Edit legend for figure 1

test <- 4

@@

**Figure 1. 5-day PEG treatment prolongs susceptibility and mice become persistently colonized with *C. difficile*.** A. Setup of the experimental timeline for subset of experiments with 5-day PEG treated mice. B. Weight change from baseline weight in groups after treatment with PEG and/or clindamycin, followed by *C. difficile* challenge. C. *C. difficile* CFU/gram stool measured over time (N = `r test`-`(insert variable name)` mice per timepoint) via serial dilutions. The black line represents the limit of detection for the first serial dilution. CFU quantification data was not available for each mouse due to stool sampling difficulties (particularly the day the mice came off of the PEG treatment) or early deaths. Lines represent the median for each source and circles represent individual mouse samples. Asterisks indicate timepoints where the weight change or CFU/g was significantly different between groups by the Kruskal-Wallis test with Benjamini-Hochberg correction for testing multiple timepoints.
\newpage

@@

one_day_samples_per_day <- metadata %>%
  filter(group == "C" & exp_num %in% c("M6")| #Only use C mice from this experiments. Allocated groups to figures based on paper outline.
             group == "1RM1" & exp_num %in% c("M6R")| #Had to differentiate experiment 6 from 6R in the metadata to create unique_mouse_id that wouldn't overlap for the M1 & 1RM1 mice that are both labeled with mouse_ids that are #s1-6
             group == "M1" & exp_num %in% c("M6")) %>%
  group_by(day) %>%
  count() 
one_day_sample_min <- min(one_day_samples_per_day$n)
one_day_sample_max <- max(one_day_samples_per_day$n)

>>>>

#Use same code from five_day_PEG_subset() in code/utilities.R to determine number of samples we had C. difficile CFU counts for per day
five_day_mice <- metadata %>% filter(group == "C" & exp_num %in% c("M3","M4", "M5", "M8")| #Only use C mice from these experiments. Allocated groups to figures based on paper outline.
             group == "WM" & exp_num %in% c("M3","M4", "M5", "M8")|
             group == "WMC" & exp_num %in% c("M3","M4")|
             group == "WMR" & exp_num %in% c("M5","M6"))
five_d_cfu <- five_day_mice %>% 
  filter(sample_type == "stool") %>% #Select only stool samples
  filter(day %in% c(0, 1, 2, 3, 4, 5, 6, 8, 9, 10, 15, 20, 25, 30)) %>%  #select timepoints on plot
  filter(!is.na(avg_cfu)) %>% #Remove rows with NA values
  group_by(day) %>% 
  count()
#Figure out min & max number of samples we had cfu counts for
five_d_cfu_n_min <- min(five_d_cfu$n)
five_d_cfu_n_max <- max(five_d_cfu$n)

@@

**Figure 1. 5-day PEG treatment prolongs susceptibility and mice become persistently colonized with *C. difficile*.** A. Setup of the experimental timeline for experiments with 5-day PEG treated mice. Clindamycin was administered at 10 mg/kg by intraperitoneal injection. 15% PEG 3350 was administered in the drinking water for five days. B. Weight change from baseline weight in groups after treatment with PEG and/or clindamycin, followed by *C. difficile* challenge. C. *C. difficile* CFU/gram stool measured over time (N = `r five_d_cfu_n_min`-`r five_d_cfu_n_max` mice per timepoint) via serial dilutions. The black line represents the limit of detection for the first serial dilution. CFU quantification data was not available for each mouse due to stool sampling difficulties (particularly the day the mice came off of the PEG treatment) or early deaths. For B-C, lines represent the median for each treatment group and circles represent samples from individual mice. Asterisks indicate timepoints where the weight change or CFU/g was significantly different between groups by the Kruskal-Wallis test with Benjamini-Hochberg correction for testing multiple timepoints.
\newpage

@@

#Use same code from one_day_PEG_subset() in code/utilities.R to determine number of samples per day
one_day_samples_per_day <- metadata %>%
  filter(group == "C" & exp_num %in% c("M6")| #Only use C mice from this experiments. Allocated groups to figures based on paper outline.
             group == "1RM1" & exp_num %in% c("M6R")| #Had to differentiate experiment 6 from 6R in the metadata to create unique_mouse_id that wouldn't overlap for the M1 & 1RM1 mice that are both labeled with mouse_ids that are #s1-6
             group == "M1" & exp_num %in% c("M6")) %>%
  group_by(day) %>%
  count() 
#To Do: this code is not specific for CFU values or the timepoints shown on panel B
one_day_sample_min <- min(one_day_samples_per_day$n)
one_day_sample_max <- max(one_day_samples_per_day$n)

### 2021-04-15 submission/manuscript.tex
Edit legend for figure 1

\textbf{Figure 1. 5-day PEG treatment prolongs susceptibility and mice
become persistently colonized with \emph{C. difficile}.} A. Setup of the
experimental timeline for subset of experiments with 5-day PEG treated
mice. B. Weight change from baseline weight in groups after treatment
with PEG and/or clindamycin, followed by \emph{C. difficile} challenge.
C. \emph{C. difficile} CFU/gram stool measured over time (N =
4-\texttt{(insert\ variable\ name)} mice per timepoint) via serial
dilutions. The black line represents the limit of detection for the
first serial dilution. CFU quantification data was not available for
each mouse due to stool sampling difficulties (particularly the day the
mice came off of the PEG treatment) or early deaths. Lines represent the
median for each source and circles represent individual mouse samples.
Asterisks indicate timepoints where the weight change or CFU/g was
significantly different between groups by the Kruskal-Wallis test with
Benjamini-Hochberg correction for testing multiple timepoints. \newpage

>>>>

\textbf{Figure 1. 5-day PEG treatment prolongs susceptibility and mice
become persistently colonized with \emph{C. difficile}.} A. Setup of the
experimental timeline for experiments with 5-day PEG treated mice.
Clindamycin was administered at 10 mg/kg by intraperitoneal injection.
15\% PEG 3350 was administered in the drinking water for five days. B.
Weight change from baseline weight in groups after treatment with PEG
and/or clindamycin, followed by \emph{C. difficile} challenge. C.
\emph{C. difficile} CFU/gram stool measured over time (N = 16-59 mice
per timepoint) via serial dilutions. The black line represents the limit
of detection for the first serial dilution. CFU quantification data was
not available for each mouse due to stool sampling difficulties
(particularly the day the mice came off of the PEG treatment) or early
deaths. For B-C, lines represent the median for each treatment group and
circles represent samples from individual mice. Asterisks indicate
timepoints where the weight change or CFU/g was significantly different
between groups by the Kruskal-Wallis test with Benjamini-Hochberg
correction for testing multiple timepoints. \newpage
